Supplementary Information

### 2015-09-03 manuscript/supplement.tex
Finished and spellchecked.

\documentclass[12pt]{article}  
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{url}
\usepackage[dvips]{graphicx}
\usepackage{multirow}
\usepackage{geometry}
\usepackage{pdflscape}
\usepackage[labelfont=bf]{caption}
\usepackage{setspace}
\usepackage[round]{natbib}
\usepackage{float}
\usepackage[running]{lineno}

@@

\title{Supplementary Information}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
\date{\footnotesize$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\
\medskip$^2$Department of Biology\\
Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
Halifax NS, B3H 4R2, Canada\\
\medskip$^3$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\}

@@

  We combined published food webs from~\cite{GlobalWeb},~\cite{Riede2011},
  and~\cite{Dunne2013}. Of the 358 food webs available
  from~\cite{GlobalWeb}, 59 were rejected because their original source was
  unpublished or could not be retrieved. We further eliminated 13 source or
  sink webs (which describe feeding links flowing from or to a particular
  resource or top predator rather than the interactions of an entire
  community), 8 plant-pollinator webs, 33 host-parasitoid webs, and 2 networks
  describing competitive interactions. Finally, we eliminated 2 webs
  describing  inferred interactions in an extinct community, 10 ``generalized
  schemes'' that were not based on direct field data, and 4 webs where it was
  not clear which of several described study sites were used to construct the
  food web (and therefore the latitude of the food web could not be
  included). This left us with 226 webs from~\cite{GlobalWeb}.

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        4     & 3 & \cite{Johnston1956}    & estuary &       & No    & Sink web \\
        5     & 3 & \cite{Teal1962}    & estuary & 31,28,38 N & Yes   &       \\
        6     & 3 & \cite{MacGinitie1935}    & estuary & 36,48,18 N & Yes   &       \\
        7     & 3 & \cite{Kremer1978}    & marine & 41,45 - 41,30 N & Yes   &       \\
        8     & 3 & \cite{Nixon1973}    & estuary & 41,33,00 N & Yes   &       \\
        9     & 3 & \cite{Kitching1967}  & stream &       & No    & Could not locate original source \\
        10    & 3 & \cite{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
        11    & 3 & \cite{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
        12    & 3 & \cite{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
        13    & 3 & \cite{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
        14    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        15    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        16    & 3 & \cite{Copeland1974}    & estuary &       & No    & Could not locate original source \\
        17    & 3 & \cite{Hiatt1960}  & marine & 4,30 - 15 N & No    & Generalized scheme \\
        18    & 3 & \cite{Niering1963a}  & terrestrial & 1,01,29 - 1,06,23 N & Yes   &       \\
        19    & 3 & \cite{Brooks1963}    & lake &       & No    & Could not locate original source \\
        20    & 3 & \cite{Knox1970}  & terrestrial &       & No    & Could not locate original source \\
        21    & 3 & \cite{Patten1979}  & marine & 70-85 S & Yes   &       \\
        22    & 3 & \cite{Summerhayes1923}  & terrestrial & 74,27,54 N & Yes   &       \\
        23    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        24    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        25    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        26    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        27    & 3 & \cite{Varley1970}  & terrestrial &       & No    & Could not locate original source \\
        28    & 3 & \cite{Paviour-Smith1956}  & estuary & 45,51,30 S & Yes   &       \\
        29    & 3 & \cite{Dunbar1953}  & marine &       & No    & Generalized scheme \\
        30    & 3 & \cite{Mackintosh1964}  & marine &       & No    & Generalized scheme \\
        31    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
      \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        32    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
        33    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        34    & 3 & \cite{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
        35    & 3 & \cite{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
        36    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        37    & 3 & \cite{Clarke1967}    & marine & 41,02,49 N & Yes   &       \\
        38    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        39    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        40    & 3 & \cite{Harrison1962}  & terrestrial &       & No    & Generalized scheme \\
        41    & 3 & \cite{Parin1970}  & marine &       & No    & Could not locate original source \\
        42    & 3 & \cite{Vinogradov1978}  & marine &       & No    & Study site unclear \\
        43    & 3 & \cite{Rosenthal1974}    & marine & 32,57 N & Yes   &       \\
        44    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        45    & 3 & \cite{Tilly1968}    & stream & 41,22,55 N & Yes   &       \\
        46    & 3 & \cite{Patten1975}    & lake & 33,54 N & Yes   &       \\
        47    & 3 & \cite{Harris1980}    & lake &       & No    & Study site unclear \\
        48    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
        49    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
        50    & 3 & \cite{Nybakken1982}    & marine &       & No    & Generalized scheme \\
        51    & 3 & \cite{Dexter1947}    & marine & 42,38,56 N & Yes   &       \\
        52    & 3 & \cite{Paine1980a}    & marine & 58,27 N & Yes   &       \\
        53    & 3 & \cite{Paine1980a}    & marine & 48,19 - 48,37 N & Yes   &       \\
        54    & 3 & Unpublished  & marine &       & No    & Unpublished \\
        55    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
        56    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
        57    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        58    & 3 & \cite{Cohen1990}  & lake & 51,46 N & Yes   &       \\
        59    & 3 & \cite{Twomey1945}    & terrestrial & 40,09,47 N & Yes   &       \\
        60    & 3 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & Yes   &       \\
        61    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        62    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        88    & 3 & \cite{Kuusela1980}  & stream &       & No    & Could not locate original source \\
        89    & 3 & \cite{Hartley1948}  & stream & 52,13 N & Yes   &       \\
        91    & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
        92    & 3 & \cite{Swan1961}  & terrestrial &       & No    & Generalized scheme \\
        93    & 3 & \cite{Pattie1966}    & terrestrial & 45 N  & Yes   &       \\
        94    & 3 & \cite{Brown1971}    & terrestrial &       & No    & Could not locate original source \\
        95    & 3 & \cite{Brown1975}    & terrestrial & 70,11,14.18 N & Yes   &       \\
        96    & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
        97    & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
        98    & 3 & \cite{Holm1980}  & terrestrial &       & No    & Could not locate original source \\
        99    & 3 & \cite{Howes1954}    & terrestrial & 32,36 N & Yes   &       \\
        100   & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
        101   & 3 & \cite{Cohen1990} & lake  &       & No    & Could not locate original source \\
        102   & 3 & \cite{Shushkina1979}  & marine & 10 S - 15 N & Yes   &       \\
        103   & 3 & \cite{Petipa1979}  & marine &       & No    & Generalized scheme \\
        104   & 3 & \cite{Menge1976}  & marine & 4,48,04 N & Yes   &       \\
        105   & 3 & \cite{Edwards1982}  & marine & 42,40 N & Yes   &       \\
        106   & 3 & \cite{Glynn1965}  & marine &       & No    & Could not locate original source \\
        107   & 3 & \cite{Peterson1979}  & marine & 39,52,02 N & Yes   &       \\
        108   & 3 & \cite{Hewatt1937}  & marine & 36,37 N & Yes   &       \\
        109   & 3 & \cite{Castilla1981} & marine &       & No    & Could not locate original source \\
        110   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
        111   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
        112   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
        113   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
        114   & 3 & \cite{Marshall1982}  & lake  & 17,54,11.90 S & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        115   & 3 & \cite{Koepcke1952}  & marine &       & No    & Could not locate original source \\
        116   & 3 & \cite{Hurlbert1972}  & lake  & 35,09,19 S & Yes   &       \\
        117   & 3 & \cite{Zaret1973}  & lake  & 9,11,31.50 N & Yes   &       \\
        118   & 3 & \cite{Bindloss1972}  & lake  & 56,41,18.71 N & Yes   &       \\
        119   & 3 & \cite{Mann1972}  & stream & 51,27 N & Yes   &       \\
        120   & 3 & \cite{Moriarty1973}  & lake  & 0,00,58 N & Yes   &       \\
        121   & 3 & \cite{VanEs1977}  & estuary & 53,20 - 53,15 N & Yes   &       \\
        122   & 3 & \cite{Nixon1973}  & estuary & 41,33,04 N & Yes   &       \\
        123   & 3 & \cite{Harris1972}  & terrestrial & 40,45,28 N & Yes   &       \\
        124   & 3 & \cite{Collins1976}  & stream & 44,34 N & Yes   &       \\
        125   & 3 & \cite{Landry1977}  & marine &       & No    & Generalized scheme \\
        126   & 3 & \cite{Larsson1978}  & lake  & 61,26,00 N & Yes   &       \\
        127   & 3 & \cite{Beaver1979}  & lake  &       & No    & Could not locate original source \\
        128   & 3 & \cite{Beaver1979}  & lake  &       & No    & Could not locate original source \\
        129   & 3 & Unpublished & terrestrial &       & No    & Unpublished \\
        130   & 3 & \cite{Odum1975}  & estuary & 27,12 N & Yes   &       \\
        131   & 3 & \cite{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
        132   & 3 & \cite{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
        133   & 3 & \cite{Beaver1985}  & lake  & 7,52,22 N & Yes   &       \\
        134   & 3 & \cite{Beaver1985}  & lake  & 19 S  & Yes   &       \\
        135   & 3 & \cite{Beaver1985}  & lake  & 4,40,46 S & Yes   &       \\
        136   & 3 & \cite{Bradshaw1983}    & lake  &       & No    & Could not locate original source \\
        137   & 3 & \cite{Corker1984}  & lake  & 22,14-22,17 N & Yes   &       \\
        138   & 3 & \cite{Kitching1983}     & lake  &       & No    & Could not locate original source \\
        139   & 3 & \cite{Kitching1983}  & lake  &       & No    & Could not locate original source \\
        140   & 3 & \cite{Seifert1979}  & terrestrial & 10,21 N & Yes   &       \\
        141   & 3 & \cite{Seifert1976}  & terrestrial &       & No    & Competition network \\
        142   & 3 & \cite{Seifert1976}  & terrestrial &       & No    & Competition network \\
        143   & 3 & \cite{Snow1958}    & lake  & 34,41,45 N & Yes   &       \\
         \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        338   & 3 & \cite{Torres2013}  & marine &       & No    & Could not locate original source \\
        339   & 3 & \cite{Bulman2001}  & marine & 37-39 S & Yes   &       \\
        340   & 3 & \cite{Smith2007}  & marine & 74-78 S & Yes   &       \\
        341   & 3 & \cite{Lancraft1991}  & marine & 58,20.8 - 60,10.4 S & Yes   &       \\
        342   & 3 & \cite{Hopkins1993}  & marine & 57,00 - 60,45 S & Yes   &       \\
        343   & 3 & \cite{Kitching1987}  & lake  & 28,12 S & Yes   &       \\
        344   & 3 & \cite{Hodkinson2004}  & terrestrial &       & No    & Host-parasitoid web \\
        345   & 3 & \cite{Boit2012}  & lake  & 47,38,10 N & Yes   &       \\
        346   & 3 & \cite{Rayner2010}  & stream & 17,7 S & Yes   &       \\
        347   & 3 & \cite{Motta2005}  & stream & 23,03 S & Yes   &       \\
        348   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        349   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        350   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        351   & 3 & \cite{Warren1989}     & lake  &       & No    & Could not locate original source \\
        352   & 3 & \cite{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
        353   & 3 & \cite{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
        354   & 3 & \cite{Goldwasser1993}  & terrestrial & 18,03 N & Yes   &       \\
        355   & 3 & \cite{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
        356   & 3 & \cite{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
        357   & 3 & \cite{Yodzis1998} & marine & 34,21 - 16 S & No    & Study site unclear \\
        358   & 3 & \cite{Schroter2003}  & terrestrial &       & No    & Generalized scheme \\
        359   & 3 & \cite{Baiser2012}  & lake  &       & No    & Study site unclear \\
        \hline
      \end{tabular}%
        }
    \end{table}%

@@

    None of our models were affected by the removal of any single food web.
    Estimates of co-efficients from all jackknifed datasets were extremely
    similar (Figs.~\ref{LS_web,Gen_web,Vul_web}). Moreover, our models were also robust to the removal
    of any given author (Figs.~\ref{LS_auth,Gen_auth,Vul_auth}). We are therefore very confident that,
    while there are undoubtedly differences in the methods used to compile food webs,
    these differences are not driving the trends we report in this study.

>>>>

\documentclass[12pt]{article}  
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{url}
\usepackage[dvips]{graphicx}
\usepackage{multirow}
\usepackage{geometry}
\usepackage{pdflscape}
\usepackage[labelfont=bf]{caption}
\usepackage{setspace}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{float}
\usepackage[running]{lineno}

@@

\title{Supplementary Information}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
\date{\footnotesize$^1$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\
\medskip$^2$Department of Biology\\
Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
Halifax NS, B3H 4R2, Canada\\}

@@

  We combined published food webs from~\cite{GlobalWeb},~\cite{Riede2011},
  and~\cite{Dunne2013}. Of the 358 food webs available
  from~\cite{GlobalWeb}, 59 were rejected because their original source was
  unpublished or could not be retrieved. We further eliminated 13 source or
  sink webs (which describe feeding links flowing from or to a particular
  resource or top predator rather than the interactions of an entire
  community), 8 plant-pollinator webs, 33 host-parasitoid webs, and 2 networks
  describing competitive interactions. Finally, we eliminated 2 webs
  describing  inferred interactions in an extinct community, 10 ``generalised
  schemes'' that were not based on direct field data, and 4 webs where it was
  not clear which of several described study sites were used to construct the
  food web (and therefore the latitude of the food web could not be
  included). This left us with 226 webs from~\cite{GlobalWeb}.

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        4     & 3 & \cite{Johnston1956}    & estuary &       & No    & Sink web \\
        5     & 3 & \cite{Teal1962}    & estuary & 31,28,38 N & Yes   &       \\
        6     & 3 & \cite{MacGinitie1935}    & estuary & 36,48,18 N & Yes   &       \\
        7     & 3 & \cite{Kremer1978}    & marine & 41,45 - 41,30 N & Yes   &       \\
        8     & 3 & \cite{Nixon1973}    & estuary & 41,33,00 N & Yes   &       \\
        9     & 3 & \cite{Kitching1967}  & stream &       & No    & Could not locate original source \\
        10    & 3 & \cite{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
        11    & 3 & \cite{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
        12    & 3 & \cite{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
        13    & 3 & \cite{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
        14    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        15    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        16    & 3 & \cite{Copeland1974}    & estuary &       & No    & Could not locate original source \\
        17    & 3 & \cite{Hiatt1960}  & marine & 4,30 - 15 N & No    & Generalised scheme \\
        18    & 3 & \cite{Niering1963a}  & terrestrial & 1,01,29 - 1,06,23 N & Yes   &       \\
        19    & 3 & \cite{Brooks1963}    & lake &       & No    & Could not locate original source \\
        20    & 3 & \cite{Knox1970}  & terrestrial &       & No    & Could not locate original source \\
        21    & 3 & \cite{Patten1979}  & marine & 70-85 S & Yes   &       \\
        22    & 3 & \cite{Summerhayes1923}  & terrestrial & 74,27,54 N & Yes   &       \\
        23    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        24    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        25    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        26    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        27    & 3 & \cite{Varley1970}  & terrestrial &       & No    & Could not locate original source \\
        28    & 3 & \cite{Paviour-Smith1956}  & estuary & 45,51,30 S & Yes   &       \\
        29    & 3 & \cite{Dunbar1953}  & marine &       & No    & Generalised scheme \\
        30    & 3 & \cite{Mackintosh1964}  & marine &       & No    & Generalised scheme \\
        31    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
      \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        32    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
        33    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        34    & 3 & \cite{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
        35    & 3 & \cite{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
        36    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        37    & 3 & \cite{Clarke1967}    & marine & 41,02,49 N & Yes   &       \\
        38    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        39    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        40    & 3 & \cite{Harrison1962}  & terrestrial &       & No    & Generalised scheme \\
        41    & 3 & \cite{Parin1970}  & marine &       & No    & Could not locate original source \\
        42    & 3 & \cite{Vinogradov1978}  & marine &       & No    & Study site unclear \\
        43    & 3 & \cite{Rosenthal1974}    & marine & 32,57 N & Yes   &       \\
        44    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        45    & 3 & \cite{Tilly1968}    & stream & 41,22,55 N & Yes   &       \\
        46    & 3 & \cite{Patten1975}    & lake & 33,54 N & Yes   &       \\
        47    & 3 & \cite{Harris1980}    & lake &       & No    & Study site unclear \\
        48    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
        49    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
        50    & 3 & \cite{Nybakken1982}    & marine &       & No    & Generalised scheme \\
        51    & 3 & \cite{Dexter1947}    & marine & 42,38,56 N & Yes   &       \\
        52    & 3 & \cite{Paine1980a}    & marine & 58,27 N & Yes   &       \\
        53    & 3 & \cite{Paine1980a}    & marine & 48,19 - 48,37 N & Yes   &       \\
        54    & 3 & Unpublished  & marine &       & No    & Unpublished \\
        55    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
        56    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
        57    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        58    & 3 & \cite{Cohen1990}  & lake & 51,46 N & Yes   &       \\
        59    & 3 & \cite{Twomey1945}    & terrestrial & 40,09,47 N & Yes   &       \\
        60    & 3 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & Yes   &       \\
        61    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        62    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        88    & 3 & \cite{Kuusela1980}  & stream &       & No    & Could not locate original source \\
        89    & 3 & \cite{Hartley1948}  & stream & 52,13 N & Yes   &       \\
        91    & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
        92    & 3 & \cite{Swan1961}  & terrestrial &       & No    & Generalised scheme \\
        93    & 3 & \cite{Pattie1966}    & terrestrial & 45 N  & Yes   &       \\
        94    & 3 & \cite{Brown1971}    & terrestrial &       & No    & Could not locate original source \\
        95    & 3 & \cite{Brown1975}    & terrestrial & 70,11,14.18 N & Yes   &       \\
        96    & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
        97    & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
        98    & 3 & \cite{Holm1980}  & terrestrial &       & No    & Could not locate original source \\
        99    & 3 & \cite{Howes1954}    & terrestrial & 32,36 N & Yes   &       \\
        100   & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
        101   & 3 & \cite{Cohen1990} & lake  &       & No    & Could not locate original source \\
        102   & 3 & \cite{Shushkina1979}  & marine & 10 S - 15 N & Yes   &       \\
        103   & 3 & \cite{Petipa1979}  & marine &       & No    & Generalised scheme \\
        104   & 3 & \cite{Menge1976}  & marine & 4,48,04 N & Yes   &       \\
        105   & 3 & \cite{Edwards1982}  & marine & 42,40 N & Yes   &       \\
        106   & 3 & \cite{Glynn1965}  & marine &       & No    & Could not locate original source \\
        107   & 3 & \cite{Peterson1979}  & marine & 39,52,02 N & Yes   &       \\
        108   & 3 & \cite{Hewatt1937}  & marine & 36,37 N & Yes   &       \\
        109   & 3 & \cite{Castilla1981} & marine &       & No    & Could not locate original source \\
        110   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
        111   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
        112   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
        113   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
        114   & 3 & \cite{Marshall1982}  & lake  & 17,54,11.90 S & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        115   & 3 & \cite{Koepcke1952}  & marine &       & No    & Could not locate original source \\
        116   & 3 & \cite{Hurlbert1972}  & lake  & 35,09,19 S & Yes   &       \\
        117   & 3 & \cite{Zaret1973}  & lake  & 9,11,31.50 N & Yes   &       \\
        118   & 3 & \cite{Bindloss1972}  & lake  & 56,41,18.71 N & Yes   &       \\
        119   & 3 & \cite{Mann1972}  & stream & 51,27 N & Yes   &       \\
        120   & 3 & \cite{Moriarty1973}  & lake  & 0,00,58 N & Yes   &       \\
        121   & 3 & \cite{VanEs1977}  & estuary & 53,20 - 53,15 N & Yes   &       \\
        122   & 3 & \cite{Nixon1973}  & estuary & 41,33,04 N & Yes   &       \\
        123   & 3 & \cite{Harris1972}  & terrestrial & 40,45,28 N & Yes   &       \\
        124   & 3 & \cite{Collins1976}  & stream & 44,34 N & Yes   &       \\
        125   & 3 & \cite{Landry1977}  & marine &       & No    & Generalised scheme \\
        126   & 3 & \cite{Larsson1978}  & lake  & 61,26,00 N & Yes   &       \\
        127   & 3 & \cite{Beaver1979}  & lake  &       & No    & Could not locate original source \\
        128   & 3 & \cite{Beaver1979}  & lake  &       & No    & Could not locate original source \\
        129   & 3 & Unpublished & terrestrial &       & No    & Unpublished \\
        130   & 3 & \cite{Odum1975}  & estuary & 27,12 N & Yes   &       \\
        131   & 3 & \cite{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
        132   & 3 & \cite{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
        133   & 3 & \cite{Beaver1985}  & lake  & 7,52,22 N & Yes   &       \\
        134   & 3 & \cite{Beaver1985}  & lake  & 19 S  & Yes   &       \\
        135   & 3 & \cite{Beaver1985}  & lake  & 4,40,46 S & Yes   &       \\
        136   & 3 & \cite{Bradshaw1983}    & lake  &       & No    & Could not locate original source \\
        137   & 3 & \cite{Corker1984}  & lake  & 22,14-22,17 N & Yes   &       \\
        138   & 3 & \cite{Kitching1983}     & lake  &       & No    & Could not locate original source \\
        139   & 3 & \cite{Kitching1983}  & lake  &       & No    & Could not locate original source \\
        140   & 3 & \cite{Seifert1979}  & terrestrial & 10,21 N & Yes   &       \\
        141   & 3 & \cite{Seifert1976}  & terrestrial &       & No    & Competition network \\
        142   & 3 & \cite{Seifert1976}  & terrestrial &       & No    & Competition network \\
        143   & 3 & \cite{Snow1958}    & lake  & 34,41,45 N & Yes   &       \\
         \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        338   & 3 & \cite{Torres2013}  & marine &       & No    & Could not locate original source \\
        339   & 3 & \cite{Bulman2001}  & marine & 37-39 S & Yes   &       \\
        340   & 3 & \cite{Smith2007}  & marine & 74-78 S & Yes   &       \\
        341   & 3 & \cite{Lancraft1991}  & marine & 58,20.8 - 60,10.4 S & Yes   &       \\
        342   & 3 & \cite{Hopkins1993}  & marine & 57,00 - 60,45 S & Yes   &       \\
        343   & 3 & \cite{Kitching1987}  & lake  & 28,12 S & Yes   &       \\
        344   & 3 & \cite{Hodkinson2004}  & terrestrial &       & No    & Host-parasitoid web \\
        345   & 3 & \cite{Boit2012}  & lake  & 47,38,10 N & Yes   &       \\
        346   & 3 & \cite{Rayner2010}  & stream & 17,7 S & Yes   &       \\
        347   & 3 & \cite{Motta2005}  & stream & 23,03 S & Yes   &       \\
        348   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        349   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        350   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        351   & 3 & \cite{Warren1989}     & lake  &       & No    & Could not locate original source \\
        352   & 3 & \cite{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
        353   & 3 & \cite{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
        354   & 3 & \cite{Goldwasser1993}  & terrestrial & 18,03 N & Yes   &       \\
        355   & 3 & \cite{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
        356   & 3 & \cite{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
        357   & 3 & \cite{Yodzis1998} & marine & 34,21 - 16 S & No    & Study site unclear \\
        358   & 3 & \cite{Schroter2003}  & terrestrial &       & No    & Generalised scheme \\
        359   & 3 & \cite{Baiser2012}  & lake  &       & No    & Study site unclear \\
        \hline
      \end{tabular}%
        }
    \end{table}%

@@

    None of our models were affected by the removal of any single food web
    or by the removal of a set of webs compiled by a common researcher (or group of
    researchers).
    Estimates of coefficients from all jackknifed datasets were extremely
    similar (Figs.~\ref{LS_web},\ref{Gen_web},\ref{Vul_web},\ref{LS_auth},\ref{Gen_auth},\ref{Vul_auth}). 
    We are therefore very confident that, while there are undoubtedly differences 
    in the methods used to compile food webs, these differences provide an
    insufficient explanation for the trends we report in this study.
